---
title: "JIW Data Clean"
output:
  pdf_document: default
  html_document: default
date: "2023-11-09"
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(readxl)
library(lubridate)
library(tidymodels)
library(grid)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(pscl)
```

# ```{r}
# percentages_merged %>% 
#   ggplot() +
#   geom_line(mapping = aes(x = sent_change, y = trade_vol_change))
# 
# percentages_merged %>%
#   ggplot() +
#   geom_line(mapping = aes(x = Date, y = sent_change), color = 'blue') +
#   geom_line(mapping = aes(x = Date, y = trade_vol_change), color = 'red') +
#   labs(y = "Percentage Changes", x = "Date") +
#   scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))
# ```


#Loading Data...
```{r}

setwd('/Users/billyswartwout/Documents/JIW/data')
getwd()

iTraxx_EUR <- read_excel(path = 'iTRAXX data.xlsx', sheet = "ITRX EUR IG CDSI GEN 5Y")
iTraxx_EUR$Date <- as.Date(iTraxx_EUR$Date)
str(iTraxx_EUR)
iTraxx_EUR <- iTraxx_EUR %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
iTraxx_EUR <- rename(iTraxx_EUR, iTraxx_EUR_Price = `Last Price`)


iTraxx_EXJP <- read_excel(path = 'iTRAXX data.xlsx', sheet = "ITRX EXJP IG CDSI GEN 5Y")
iTraxx_EXJP <- iTraxx_EXJP %>% select(Date, `Last Price`)
iTraxx_EXJP$Date <- as.Date(iTraxx_EXJP$Date)
str(iTraxx_EXJP)
iTraxx_EXJP <- iTraxx_EXJP %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
iTraxx_EXJP <- rename(iTraxx_EXJP, iTraxx_EXJP_total = `Last Price`)


iTraxx_AUS <- read_excel(path = 'iTRAXX data.xlsx', sheet = 'ITRX AUS CDSI GEN 5Y')
iTraxx_AUS <- iTraxx_AUS %>% select(Date, `Last Price`)
iTraxx_AUS$Date <- as.Date(iTraxx_AUS$Date)
iTraxx_AUS <- iTraxx_AUS %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
iTraxx_AUS <- rename(iTraxx_AUS, iTraxx_AUS_total = `Last Price`)


iTraxx_JPN <- read_excel(path = 'iTRAXX data.xlsx', sheet = 'ITX JAPAN CDSI GEN 5Y')
iTraxx_JPN <- iTraxx_JPN %>% select(Date, `Last Price`)
iTraxx_JPN$Date <- as.Date(iTraxx_JPN$Date)
iTraxx_JPN <- iTraxx_JPN %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
iTraxx_JPN <- rename(iTraxx_JPN, iTraxx_JPN_total = `Last Price`)

CDX_NA <- read_excel(path = 'iTRAXX data.xlsx', sheet = 'CDX IG CDSI GEN 5Y NA')
CDX_NA$Date <- as.Date(CDX_NA$Date)
CDX_NA <- CDX_NA %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
CDX_NA <- rename(CDX_NA, CDX_NA_Price = `Last Price`)

CDX_EM <- read_excel(path = 'iTRAXX data.xlsx', sheet = 'CDX EM')
CDX_EM$Date <- as.Date(CDX_EM$Date)
CDX_EM <- CDX_EM %>% filter(Date >= "2023-01-01" & Date <= "2023-09-01")
CDX_EM <- rename(CDX_EM, CDX_EM_Price = `Last Price`)

sentiment <- read_excel(path = "Sentiment Data.xlsx", sheet = "cleaned")
sentiment
str(sentiment)
sentiment$RPA_DATE_UTC <- as.Date(sentiment$RPA_DATE_UTC)
sentiment$month <- month(sentiment$RPA_DATE_UTC)
sentiment <- sentiment %>% filter(RPA_DATE_UTC >= "2023-01-01" & RPA_DATE_UTC <= "2023-09-01")
sentiment$Date = sentiment$RPA_DATE_UTC

sentiment_percent <- read_excel(path = "Sentiment Data.xlsx", sheet = "percent_change")
sentiment_percent$Date <- as.Date(sentiment_percent$Date, format = "%m/%d%Y")
str(sentiment_percent)

```

# Data Manipulation/Analysis
```{r}
percentages_merged <- merge(iTraxx_EUR, sentiment_percent)
percentages_merged <- merge(iTraxx_AUS, percentages_merged)
percentages_merged <- merge(iTraxx_EXJP, percentages_merged)
percentages_merged <- merge(iTraxx_JPN, percentages_merged)
percentages_merged <- merge(CDX_NA, percentages_merged)
percentages_merged <- merge(CDX_EM, percentages_merged)
percentages_merged <- merge(sentiment, percentages_merged)

percentages_merged = percentages_merged %>% 
  group_by(Date) %>% 
  mutate(pos_sent = mean(EVENT_SENTIMENT_SCORE[EVENT_SENTIMENT_SCORE > 0], 
                         na.rm = TRUE), 
         neg_sent = mean(EVENT_SENTIMENT_SCORE[EVENT_SENTIMENT_SCORE < 0], na.rm = TRUE),
         pos_prop = mean(EVENT_SENTIMENT_SCORE > 0, na.rm = TRUE),
         neg_prop = mean(EVENT_SENTIMENT_SCORE < 0, na.rm = TRUE)) %>% ungroup()

# percentages_merged <- rename(percentages_merged, trade_vol_change = Per_change)

percentages_merged$logfreq <- log(percentages_merged$Frequency)
percentages_merged$log_iTraxx_EUR <- log(percentages_merged$iTraxx_EUR_Price)
percentages_merged$log_iTraxx_EXJP <- log(percentages_merged$iTraxx_EXJP_total)
percentages_merged$log_iTraxx_AUS <- log(percentages_merged$iTraxx_AUS_total)
percentages_merged$log_iTraxx_JPN <- log(percentages_merged$iTraxx_JPN_total)
percentages_merged$log_CDX_NA <- log(percentages_merged$CDX_NA_Price)
percentages_merged$log_CDX_EM <- log(percentages_merged$CDX_EM_Price)
# percentages_merged$log_pos_sent_freq <- log(percentages_merged$pos_sent_freq)
# percentages_merged$log_neg_sent_freq <- log(percentages_merged$neg_sent_freq)

```
# Scaled Plot
```{r}
collapse = as.Date("2023-03-09")
timeframe = data.frame(x0 = as.Date("2022-12-26"), collapse, x1 = as.Date("2023-09-11"))

summary(percentages_merged)
prior <- percentages_merged %>% filter(Date < "2023-03-09")
meanEUR_prior = mean(prior$log_iTraxx_EUR)
meanAUS_prior = mean(prior$log_iTraxx_AUS)
meanJPN_prior = mean(prior$log_iTraxx_JPN)
meanEXJP_prior = mean(prior$log_iTraxx_EXJP)
meanNA_prior = mean(prior$log_CDX_NA)
meanEM_prior = mean(prior$log_CDX_EM)
post <- percentages_merged %>% filter(Date >= "2023-03-09")
meanEUR_post = mean(post$log_iTraxx_EUR)
meanAUS_post = mean(post$log_iTraxx_AUS)
meanJPN_post = mean(post$log_iTraxx_JPN)
meanEXJP_post = mean(post$log_iTraxx_EXJP)
meanNA_post = mean(post$log_CDX_NA)
meanEM_post = mean(post$log_CDX_EM)
meansent_prior = mean(prior$logfreq)
meansent_post = mean(post$logfreq)

# Plot for log_iTraxx_EUR_total
p1 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_iTraxx_EUR)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("EUR iTraxx Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) + 
  geom_vline(xintercept = as.numeric(collapse), 
             linetype = "solid", color = "hotpink") +
  geom_segment(aes(x = x0, y = as.numeric(meanEUR_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanEUR_post), xend = x1), data = timeframe)


# Plot for log_iTraxx_EXJP_total
p2 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_iTraxx_EXJP)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("EXJP iTraxx Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
  geom_segment(aes(x = x0, y = as.numeric(meanEXJP_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanEXJP_post), xend = x1), data = timeframe)

# Plot for log_iTraxx_AUS_total
p3 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_iTraxx_AUS)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("AUS iTraxx Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
  geom_segment(aes(x = x0, y = as.numeric(meanAUS_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanAUS_post), xend = x1), data = timeframe)

# Plot for log_iTraxx_JPN_total
p4 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_iTraxx_JPN)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("JPN iTraxx Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
  geom_segment(aes(x = x0, y = as.numeric(meanJPN_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanJPN_post), xend = x1), data = timeframe)

# Plot for log_CDX_NA
p5 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_CDX_NA)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("NA CDX Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
   geom_segment(aes(x = x0, y = as.numeric(meanNA_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanNA_post), xend = x1), data = timeframe)

# Plot for log_EM
p6 <- percentages_merged %>%  
  ggplot(aes(x = Date, y = log_CDX_EM)) +
  geom_line(size = 0.3, color = 'black') +
  labs(y = NULL, x = NULL) +
  ggtitle("EM CDX Index") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.title.x = element_blank()) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
  geom_segment(aes(x = x0, y = as.numeric(meanEM_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meanEM_post), xend = x1), data = timeframe)

# Plot for logfreq
p7 <- percentages_merged %>%
  ggplot(aes(x = Date, y = logfreq)) +
  geom_line(size = 0.3, color = 'red') +
  labs(y = NULL, x = "Date") +
  ggtitle("SVB Sentiment Changes") +
  scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_vline(xintercept = as.numeric(collapse), linetype = "solid", color = "hotpink")+
  geom_segment(aes(x = x0, y = as.numeric(meansent_prior), xend = collapse), data = timeframe) +
  geom_segment(aes(x = collapse, y = as.numeric(meansent_post), xend = x1), data = timeframe)

# print(p1)
# print(p2)

grid.newpage()
grid.draw(rbind(ggplotGrob(p1), 
                ggplotGrob(p2), 
                ggplotGrob(p3), 
                ggplotGrob(p4), 
                ggplotGrob(p5), 
                ggplotGrob(p6), 
                ggplotGrob(p7), 
                size = "last"))

```


```{r}
percentages_merged <- pivot_longer(percentages_merged, cols = c(23:28), names_to = "log_index", values_to = "log_prices")
percentages_merged <- pivot_longer(percentages_merged, cols = c(10:15), names_to = "index", values_to = "prices")
percentages_merged = percentages_merged %>% select(c(1, 7, 10, 12:20))
clean <- percentages_merged %>% select(c(1, 3:12)) %>% distinct()


# weekly regression setup
weekly <- percentages_merged %>% select(1, 4:8, 11, 12) %>% distinct() %>% group_by(week = week(Date))
weekly <- weekly %>% group_by(index, week) %>% summarise(pdiff = max(prices) - min(prices))
weekly$week = as.factor(weekly$week)
summary(weekly)

#monthly regression setup
monthly <- percentages_merged %>% select(1, 4:8, 11, 12) %>% distinct() %>% group_by(month = month(Date))
monthly <- monthly %>% group_by(index, month) %>% summarise(pdiff = max(prices) - min(prices))
monthly$month = as.factor(monthly$month)
```


#Regressions 
```{r}
mod1 <- lm(log_prices ~ Frequency + 
                  neg_prop + pos_prop + 
                  neg_sent + pos_sent + 
                  factor(log_index) +
                  Frequency*neg_prop +
                  Frequency*pos_prop, data = clean)

tab_model(mod1, p.style = "stars", digits = 4, pred.labels = c("Intercept", "Frequency", "Neg Proportion", "Pos Proportion", "Neg Sentiment", "Pos Sentiment", "CDX NA", "iTraxx AUS", "iTraxx EUR", "iTraxx EXJP", "iTraxx JPN", "Freq:Neg Proportion", "Freq: Pos Proportion"), dv.labels = "Log Prices", string.ci = "Conf. Int (95%)")



week_mod1 <- lm(pdiff ~ factor(week) + factor(index), data = weekly)
tab_model(week_mod1, pred.labels = c("(Intercept)", "1/9 - 1/13", "1/16-1/20", "1/23 - 1/27", "1/30 - 2/3", "2/6 - 2/10", "2/13 - 2/17", "2/20 - 2/24", "2/27 - 3/3", "3/6 - 3/10", "3/13 - 3/17", "3/20 - 3/24", "3/27 - 3/31", "4/3 - 4/6", "4/11 - 4/14", "4/17 - 4/21", "4/24 - 4/28", "5/2 - 5/5", "5/9 - 5/12", "5/15 - 5/19", "5/22 - 5/26", "5/30 - 6/2", "6/5 - 6/9", "6/12 - 6/16", "6/19 - 6/23", "6/26 - 6/30", "7/3 - 7/7", "7/10 - 7/14", "7/17 - 7/21", "7/24 - 7/28", "7/31 - 8/04", "8/7 - 8/11", "8/14 - 8/18", "8/21 - 8/25", "8/29 - 9/1", "CDX NA", "iTraxx AUS", "iTraxx EUR", "iTraxx EXJP", "iTraxx JPN"),
  dv.labels = "Credit Default Swap Spreads",
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)", p.style = "stars", digits = 3)


week_mod2 <- lm(pdiff ~ factor(index), data = weekly)
tab_model(week_mod2, pred.labels = c("(Intercept)", "CDX NA", "iTraxx AUS", "iTraxx EUR", "iTraxx EXJP", "iTraxx JPN"),
  dv.labels = "Credit Default Swap Spreads",
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)", p.style = "stars", digits = 3)






month_mod <- lm(pdiff ~ factor(month) + factor(index), data = monthly)
tab_model(month_mod, pred.labels = c("Intercept", "Febuary", "March", "April", "May", "June", "July", "August", "September","CDX NA", "iTraxx AUS", "iTraxx EUR", "iTraxx EXJP", "iTraxx JPN"),
  dv.labels = "Credit Default Swap Spreads",
  string.pred = "Coeffcient",
  string.ci = "Conf. Int (95%)", p.style = "stars", digits = 3)

```
# Monthly regression graphs
```{r}
monthly$predicted_pdiff <- predict(month_mod, newdata = monthly)
path_data <- data.frame()
for (index_value in unique(monthly$index)) {
  index_data <- monthly[monthly$index == index_value, ]
  path_data <- rbind(path_data, index_data)
}
custom_labels <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep")
ggplot(monthly, aes(x = factor(month), y = pdiff)) +
  geom_point() + # Add observed data points, colored by index
  geom_path(data = path_data, aes(group = index), linetype = "dashed") + 
  facet_wrap(~ factor(index), scales = "free_x") + # Create a separate plot for each index
  labs(x = "Month", y = "CDS Spread", color = "Index") + # Set axis and legend labels
  scale_x_discrete(labels = custom_labels) + # Add custom x-axis labels
  theme_minimal() + # Use a minimal theme for the plot
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1)) +
  geom_vline(xintercept = c(3), color = "red")

```
# Weekly regression graphs
```{r}

weekly$predicted_pdiff <- predict(week_mod, newdata = weekly)
path_data <- data.frame()
for (index_value in unique(weekly$index)) {
  index_data <- weekly[weekly$index == index_value, ]
  path_data <- rbind(path_data, index_data)
}

# ggplot(weekly, aes(x = factor(week), y = pdiff)) +
#   geom_point() + # Add observed data points, colored by index
#   geom_path(data = path_data, aes(group = index), linetype = "dashed") +
#   facet_wrap(~ factor(index), scales = "free_x") + # Create a separate plot for each index
#   labs(x = "Week", y = "CDS Spread", color = "Index") + # Set axis and legend labels
#   scale_x_discrete(labels = NULL) + # Add custom x-axis labels
#   ggtitle("CDS spreads by Week and Index") + # Set title
#   theme_minimal() + # Use a minimal theme for the plot
#   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + # Rotate x-axis labels for readability
#   geom_vline(xintercept = c(10), color = "red")

# Define custom labels for x-axis
custom_labels <- c("1/3 - 1/6", "1/9 - 1/13", "1/16 - 1/20", "1/23 - 1/27", "1/30 - 2/3", "2/6 - 2/10", "2/13 - 2/17", "2/20 - 2/24", "2/27 - 3/3", "3/6 - 3/10", "3/13 - 3/17", "3/20 - 3/24", "3/27 - 3/31", "4/3 - 4/6", "4/11 - 4/14", "4/17 - 4/21", "4/24 - 4/28", "5/2 - 5/5", "5/9 - 5/12", "5/15 - 5/19", "5/22 - 5/26", "5/30 - 6/2", "6/5 - 6/9", "6/12 - 6/16", "6/19 - 6/23", "6/26 - 6/30", "7/3 - 7/7", "7/10 - 7/14", "7/17 - 7/21", "7/24 - 7/28", "7/31 - 8/04", "8/7 - 8/11", "8/14 - 8/18", "8/21 - 8/25", "8/29 - 9/1")

# Create a new column indicating whether each observation belongs to the second row within each set of three graphs
weekly$second_row <- rep(c(T, F, T, F), length.out = nrow(weekly))



ggplot(weekly, aes(x = factor(week), y = pdiff)) +
  geom_point() + # Add observed data points, colored by index
  geom_path(data = path_data, aes(group = index), linetype = "dashed") +
  facet_wrap(~ factor(index), scales = "free_x", ncol = 2) + # Create a separate plot for each index with one column (and thus three rows)
  labs(x = "Week", y = "CDS Spread", color = "Index") + # Set axis and legend labels
  scale_x_discrete(labels = function(x) ifelse(weekly$second_row[as.numeric(x)], custom_labels[as.numeric(x)], "")) + # Add custom x-axis labels for the second row within each set of three graphs
  theme_minimal() + # Use a minimal theme for the plot
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + # Rotate x-axis labels for readability
  geom_vline(xintercept = c(10), color = "red")



ggplot(weekly, aes(x = factor(week), y = pdiff)) +
  geom_point() + # Add observed data points, colored by index
  geom_path(data = path_data, aes(group = index), linetype = "dashed") +
  facet_wrap(~ factor(index), scales = "free_x", ncol = 2) + # Create a separate plot for each index with one column (and thus three rows)
  labs(x = "Week", y = "CDS Spread", color = "Index") + # Set axis and legend labels
  scale_x_discrete(labels = function(x) ifelse(weekly$second_row[as.numeric(x)], custom_labels[as.numeric(x)], "")) + # Add custom x-axis labels for the second row within each set of three graphs
  theme_minimal() + # Use a minimal theme for the plot
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1), # Rotate x-axis labels for readability
        strip.text = element_text(size = 10, face = "bold")) + # Modify facet labels
  geom_vline(xintercept = c(10), color = "red")
```


# Sentiment Changes
```{r}
sentiment %>%
  ggplot() +
  geom_point(mapping = aes(x = Date, y = EVENT_SENTIMENT_SCORE), shape = 1, alpha = 0.5) +
  labs(y = "Sentiment Scores", x = "Date") +
  geom_vline(xintercept = as.numeric(as.Date("2023-03-10")), color = "red")

```

# Frequency of Sentiment Releases
```{r}
# freq_data <- sentiment %>% 
#   select(Date, EVENT_SENTIMENT_SCORE) %>% 
#   group_by(Date) %>% mutate(freq = n()) %>% select(Date, freq) %>% unique()
# 
# freq_data %>% 
#   ggplot() +
#   geom_line(mapping = aes(x = Date, y = freq)) +
#   labs(y = "Frequency of Sentiment Releases", x = "Date")
```

```{r}
# percentages_merged %>%
#   ggplot() +
#   geom_line(mapping = aes(x = Date, y = sent_change, color = "Sent Change"), size = 0.5) +
#   geom_line(mapping = aes(x = Date, y = trade_vol_change, color = "Trade Volume Change"), size = 0.5) +
#   labs(y = "Volume Change (%)", x = "Date") +
#   ggtitle("iTraxx/ SVB Sentiment Changes") +
#   scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_color_manual(values = c("blue", "red"), labels = c("Sentiment Change", "Trade Volume Change")) +
#   labs(color = "Change Type")
```

# Unscaled plot
```{r}
# percentages_merged %>%
#   ggplot() +
#   geom_line(mapping = aes(x = Date, y = logfreq, color = "Sent Change"), size = 0.5) +
#   geom_line(mapping = aes(x = Date, y = log_prices, color = "Trade Volume Change"), size = 0.5) +
#   labs(y = "Log Volume Change", x = "Date") +
#   ggtitle("iTraxx/ SVB Sentiment Changes") +
#   scale_x_date(date_breaks = "1 month", date_labels = "%b %d") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
#   scale_color_manual(values = c("blue", "red"), labels = c("Sentiment Change", "Trade Volume Change")) +
#   labs(color = "Change Type")
```


#Other data tables
# ```{r}
# formattable(meanEUR_prior, meanAUS_prior, meanJPN_prior, meanEXJP_prior,
# meanNA_prior,meanEM_prior, meanEUR_post, meanAUS_post, meanJPN_post, meanEXJP_post, meanNA_post, meanEM_post)
# ```


# percentages_merged$log_iTraxx_EUR_lag1_month <- dplyr::lag(percentages_merged$log_iTraxx_EUR, n = 30)
# percentages_merged$Date_lagged <- percentages_merged$Date - 30
# percentages_merged$log_iTraxx_EUR_lag1_week <- dplyr::lag(percentages_merged$log_iTraxx_EUR, n = 7)
# 
# percentages_merged$log_iTraxx_AUS_lag1_month <- dplyr::lag(percentages_merged$log_iTraxx_AUS, n = 30)
# percentages_merged$Date_lagged <- percentages_merged$Date - 30
# percentages_merged$log_iTraxx_AUS_lag1_week <- dplyr::lag(percentages_merged$log_iTraxx_AUS, n = 7)
# 
# percentages_merged$log_iTraxx_JPN_lag1_month <- dplyr::lag(percentages_merged$log_iTraxx_JPN, n = 30)
# percentages_merged$Date_lagged <- percentages_merged$Date - 30
# percentages_merged$log_iTraxx_JPN_lag1_week <- dplyr::lag(percentages_merged$log_iTraxx_JPN, n = 7)
# 
# percentages_merged$log_iTraxx_EXJP_lag1_month <- dplyr::lag(percentages_merged$log_iTraxx_EXJP, n = 30)
# percentages_merged$Date_lagged <- percentages_merged$Date - 30
# percentages_merged$log_iTraxx_EXJP_lag1_week <- dplyr::lag(percentages_merged$log_iTraxx_EXJP, n = 7)


# ```{r}
# EUR_model_neg <- lm(log_iTraxx_EUR ~ logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# EUR_model_pos <- lm(log_iTraxx_EUR ~ logfreq + pos_sent_freq + pos_sent, data = percentages_merged)
# 
# summary(EUR_model_neg)
# 
# AUS_model_neg <- lm(log_iTraxx_AUS ~ logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# AUS_model_pos <- lm(log_iTraxx_AUS ~ logfreq + pos_sent_freq + pos_sent, data = percentages_merged)
# 
# JPN_model_neg <- lm(log_iTraxx_JPN ~ logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# JPN_model_pos <- lm(log_iTraxx_JPN ~ logfreq + pos_sent_freq + pos_sent, data = percentages_merged)
# 
# EXJP_model_neg <- lm(log_iTraxx_EXJP ~ logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# EXJP_model_pos <- lm(log_iTraxx_EXJP ~ logfreq + pos_sent_freq + pos_sent, data = percentages_merged)
# 
# tab_model(EUR_model_neg, EUR_model_pos, p.style = "stars", digits = 4, show.std = TRUE)
# tab_model(AUS_model_neg, AUS_model_pos, p.style = "stars", digits = 4, show.std = TRUE)
# tab_model(JPN_model_neg, JPN_model_pos, p.style = "stars", digits = 4, show.std = TRUE)
# tab_model(EXJP_model_neg, EXJP_model_pos, p.style = "stars", digits = 4, show.std = TRUE)
# 
# tab_model(EUR_model_neg, EUR_model_pos, 
#           AUS_model_neg, AUS_model_pos, 
#           JPN_model_neg, JPN_model_pos, 
#           EXJP_model_neg, EXJP_model_pos, 
#           p.style = "stars", 
#           show.std = TRUE)
# 
# ```

# Lagged Regressions
# ```{r}
# EUR_model_neg_lagged <- lm(log_iTraxx_EUR ~ log_iTraxx_EUR_lag1_week + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# EUR_model_neg_lagged2 <- lm(log_iTraxx_EUR ~ log_iTraxx_EUR_lag1_month + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# 
# AUS_model_neg_lagged <- lm(log_iTraxx_AUS ~ log_iTraxx_AUS_lag1_week + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# AUS_model_neg_lagged2 <- lm(log_iTraxx_AUS ~ log_iTraxx_AUS_lag1_month + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# 
# JPN_model_neg_lagged <- lm(log_iTraxx_JPN ~ log_iTraxx_JPN_lag1_week + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# JPN_model_neg_lagged2 <- lm(log_iTraxx_JPN ~ log_iTraxx_JPN_lag1_month + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# 
# EXJP_model_neg_lagged <- lm(log_iTraxx_EXJP ~ log_iTraxx_EXJP_lag1_week + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# EXJP_model_neg_lagged2 <- lm(log_iTraxx_EXJP ~ log_iTraxx_EXJP_lag1_month + logfreq + neg_sent_freq + neg_sent, data = percentages_merged)
# 
# 
# tab_model(EUR_model_neg_lagged, EUR_model_neg_lagged2, EUR_model_neg, p.style = "stars", digits = 4)
# tab_model(AUS_model_neg_lagged, AUS_model_neg_lagged2, AUS_model_neg, p.style = "stars", digits = 4)
# tab_model(JPN_model_neg_lagged, JPN_model_neg_lagged2, JPN_model_neg, p.style = "stars", digits = 4)
# tab_model(EXJP_model_neg_lagged, EXJP_model_neg_lagged2, EXJP_model_neg, p.style = "stars", digits = 4)
# 
# ```


